---
title: "Boardgame Analysis"
author: "Ryan Harrington"
date: "4/4/2022"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: yeti
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(janitor)

# install.packages("janitor")

```

```{r}
boardgames <-
  read_csv2(here::here("Data", "bgg_dataset.csv"))
```

```{r}
source(here::here("Scripts", "01_Clean_Boardgames.R"))
```

```{r}
boardgames_clean <- clean_names(boardgames_clean)
```
How many boardgames were published each year?

```{r}
boardgames_clean %>% 
  count(year_published, sort = T) %>% 
  ggplot(aes(x = year_published,
             y = n)) +
  geom_line()
```

What does `rating_average` look like?

```{r}
boardgames_clean %>% 
  ggplot(aes(x = rating_average)) +
  geom_histogram()
```

```{r}
boardgames_clean %>% 
  filter(year_published <= 0) %>% 
  arrange(year_published)
```

```{r}
boardgames_clean <-
  boardgames_clean %>% 
  mutate(year_published = if_else(condition = year_published == 0,
                                  true = NA_real_,
                                  false = year_published))
```

```{r}
boardgames_clean %>% 
  mutate(players_greater_flag = if_else(max_players >= min_players,
                                        T,
                                        F)) %>% 
  filter(! players_greater_flag) %>% 
  select(id, name, min_players, max_players)
```

If `max_players` is equivalent to 0, then replace it with 999. Otherwise, return the original value.

```{r}
boardgames_clean <- 
  boardgames_clean %>% 
  mutate(max_players = if_else(max_players == 0, 999, max_players))
```

```{r}
boardgames_clean %>% 
  ggplot(aes(x = complexity_average)) +
  geom_histogram()

boardgames_clean %>% 
  mutate(play_time = log10(play_time)) %>%
  ggplot(aes(x = play_time)) +
  geom_histogram()


```

```{r}
boardgames_owned_user <- 
  boardgames_clean %>% 
  mutate(owned_users_log10 = log10(owned_users)) %>% 
  select(id, name, owned_users, owned_users_log10)

boardgames_owned_user %>%
  ggplot(aes(x = owned_users_log10)) +
  geom_histogram()
```

```{r}
summary(boardgames_clean)
```

# Imputation

If `play_time` is a `NA`, then replace it with the median, otherwise leave the original value.

```{r}
boardgames_clean <- 
  boardgames_clean %>% 
  mutate(play_time = if_else(is.na(play_time), 
                             median(play_time, na.rm = T),
                             play_time),
         owned_users = if_else(is.na(owned_users),
                               median(owned_users, na.rm = T),
                               owned_users))
```

```{r}
# boardgames_clean %>% 
#   mutate(owned_users = replace_na(owned_users, median(owned_users, na.rm = T)))
```

# Multiple conditions

* Any games with a `play_time` less than 30 minutes should be considered "fast games"
* Any games with a `play_time` between 30 minutes and 120 minutes should be considered "average games"
* Any games with a `play_time` greater than 120 minutes should be considered "long games"

```{r}
boardgames_clean %>% 
  ggplot(aes(x = play_time)) +
  geom_histogram() +
  scale_x_continuous(trans = "log10")
```

```{r}
boardgames_clean <- 
  boardgames_clean %>% 
  mutate(play_time_bins = case_when(
    play_time <= 30 ~ "fast game",
    play_time > 30 & play_time <= 120 ~ "average game",
    play_time > 120 ~ "long game"
  ))
```

* Any games with `max_players` of 3 or less should be considered "small games"
* Any games with `max_players` between 3 and 5 should be considered "medium games"
* Any games with `max_players` between 5 and 10 should be considered "large games"
* Any games with `max_players` greater than 10 should be considered "huge games"

```{r}
boardgames_clean <- 
  boardgames_clean %>% 
  mutate(max_players_bins = case_when(
    max_players <= 3 ~ "small",
    max_players > 3 & max_players <= 5 ~ "medium",
    max_players > 5 & max_players <= 10 ~ "large",
    max_players > 10 ~ "huge"
  ))
```

```{r}
boardgames_clean %>% 
  mutate(mechanic_cooperative_game = if_else(is.na(mechanic_cooperative_game), F, T)) %>% 
  count(mechanic_cooperative_game)
```

```{r}
boardgames_clean %>% glimpse()
```


# `across`

```{r}
boardgames_clean <- 
  boardgames_clean %>% 
  mutate(across(starts_with("mechanic"), ~ if_else(is.na(.), F, T)))
```

```{r}
boardgames_clean <- 
  boardgames_clean %>% 
  mutate(across(starts_with("domain"), ~if_else(is.na(.), F, T)))
```

## Practicing with logs

play_time, owned_users

```{r}
# boardgames_clean <- 
  boardgames_clean %>% 
  mutate(across(c(play_time, owned_users), ~log10(.), .names = "{.col}_log"))
```

# `across` in `summarize`

```{r}
boardgames_clean %>% 
  summarize(across(c(where(is.double), -id), ~median(., na.rm = T)))
```

```{r}
boardgames_clean %>% 
  group_by(play_time_bins, max_players_bins) %>% 
  summarize(across(c(where(is.double), -id), ~median(., na.rm = T))) %>% 
  ungroup()
```

```{r}
boardgames_clean %>% 
  summarize(across(everything(), ~sum(is.na(.))))
```

# Let's make prettier graphs

```{r}
boardgames_year <- 
  boardgames_clean %>% 
  count(year_published)
```

```{r}
boardgames_year %>% 
  ggplot(aes(x = year_published,
             y = n)) +
  geom_line(color = "blue",
            size = 1) +
  coord_cartesian(xlim = c(1900, 2020)) +
  scale_x_continuous(breaks = seq(1900, 2020, 10)) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Year Published",
       y = "Count",
       title = "Count of Boardgames Published by Year",
       subtitle = "Based upon data from Board Game Geek",
       caption = "via boardgamegeek.com") +
  theme_minimal() +
  theme(axis.title = element_text(face = "bold",
                                  size = 10))
```

